Plot estimates of pi0

### 2016-12-20 analysis/plot_cdf_eg.Rmd
plot_pi0est.Rmd script succesfully runs; next need to knit.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

```{r}
library(plyr)
library(dplyr)
library(dscr)
library(magrittr)
library(ashr)
library(ggplot2)
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
load("../output/dsc-shrink-files/res.RData")

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(dscr)
library(magrittr)
library(ashr)
library(ggplot2)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

```{r}
load("../output/dsc-shrink-files/res.RData")

### 2016-12-20 analysis/plot_lfsr.Rmd
plot_pi0est.Rmd script succesfully runs; next need to knit.

```{r chunk-options, include=FALSE}
library(dplyr)
library(ggplot2)
source("chunk-options.R")
```

@@

```{r}
load("../output/dsc-shrink-files/res.RData")
source("../R/set_plot_colors.R")

>>>>

```{r chunk_options, include=FALSE}
library(dplyr)
library(ggplot2)
source("chunk-options.R")
source("../R/set_plot_colors.R")
```

@@

```{r}
load("../output/dsc-shrink-files/res.RData")

### 2016-12-20 analysis/plot_pi0est.Rmd
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.
plot_pi0est.Rmd script succesfully runs; next need to knit.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

```{r plot_pi0est, dev='pdf', crop=TRUE}
load("../output/dsc-shrink-files/res.RData")
source("../R/set_plot_colors.R")
library(dplyr)

PLOTMETHODS= c("mixfdr.tnull","ash.n","ash.u","qvalue","locfdr")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","big-normal","bimodal")
PLOTNAMES = PLOTSCENARIOS
ALPHALEVEL = 0.8 # controls transparency

df = res$pi0_score %>% filter(scenario %in% PLOTSCENARIOS) %>% filter(method %in% PLOTMETHODS)
df$scenario = factor(df$scenario,levels=PLOTSCENARIOS)
levels(df$scenario)= PLOTNAMES

pi0_plot=ggplot(df,
         aes(pi0,pi0_est,colour=method,alpha=ALPHALEVEL)) +geom_point(shape=1) +
  facet_grid(. ~ scenario) + 
  guides(alpha=FALSE) +
  geom_abline(colour = "black") +
  xlab("True pi0") +
  ylab("Estimated pi0") 
print(pi0_plot +scale_y_continuous(limits=c(0,1)) +
        scale_x_continuous(limits=c(0,1)) +
        #scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels) +
        coord_equal(ratio=1) + colScale + theme(legend.position = "top",axis.text.x = element_text(size = 8,angle=45)))

```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(magrittr)
library(dplyr)
source("chunk-options.R")
source("../R/set_plot_colors.R")
```

*Explain here what this chunk does.*

```{r plot_pi0est, dev='pdf', crop=TRUE}
load("../output/dsc-shrink-files/res.RData")

PLOTMETHODS   = c("mixfdr.tnull","ash.n","ash.u","qvalue","locfdr")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal")
PLOTNAMES     = PLOTSCENARIOS
ALPHALEVEL    = 0.8 # controls transparency

df = res$pi0_score %>% 
       filter(scenario %in% PLOTSCENARIOS) %>% 
       filter(method %in% PLOTMETHODS)
df$scenario = factor(df$scenario,levels=PLOTSCENARIOS)
levels(df$scenario) = PLOTNAMES

pi0_plot = ggplot(df,aes(pi0,pi0_est,colour = method,alpha = ALPHALEVEL)) +
  geom_point(shape = 1) +
  facet_grid(. ~ scenario) + 
  guides(alpha = FALSE) +
  geom_abline(colour = "black") +
  xlab("True pi0") +
  ylab("Estimated pi0") 
print(pi0_plot + scale_y_continuous(limits = c(0,1.01)) +
        scale_x_continuous(limits = c(0,1.01)) +
        coord_equal(ratio = 1) + 
        colScale + 
        theme(legend.position = "top",
              axis.text.x     = element_text(size = 8,angle = 45)))
```
